---
title: "IPseq"
author: "Rebecca Halbach"
contact: "rebecca.halbach@radboudumc.nl"
date: "27/04/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path='Figs/')
```

### Goal
This script will analyse the enrichment of tapiR1/2 piRNAs reads in the endogenous PIWI-IP. Samples used for that were:

* RDVJ106: input, uninfected
* RDVJ101: empty IP, uninfected
* RDVJ102: Ago3 IP, uninfected
* RDVJ103: Piwi4 IP, uninfected
* RDVJ104: Piwi5 IP, uninfected
* RDVJ105: Piwi6 IP, uninfected  

Input files can be generated with:  
AnalysisIPseq.sh  

  
#### Load required libraries

Requires the following package:

* tidyverse 1.2.1  

```{r}
library(tidyverse)

```


#### Load files for tapiR1

```{r}
Dir  = "./IPseq/Raw"  #change to folder with data
FilePath = dir("./IPseq/Raw/", "*tapiR1")

tapiR1Files=file.path(Dir, FilePath)

names=c("4_Ago3", "1_Piwi4", "2_Piwi5", "3_Piwi6")

names(tapiR1Files)= names


for (i in 1:length(tapiR1Files)){
          x= read_tsv(tapiR1Files[i], col_names = TRUE) 
          y= log2(sum(sum(x$Count_IP)/ sum(x$Count_input)))
          assign(paste(names(tapiR1Files)[i], "tapiR1", sep="_"), y)
}

```

#### Load files for tapiR2
```{r}
Dir  = "./IPseq/Raw"  #change to folder with data
FilePath = dir("./IPseq/Raw/", "*tapiR2")

tapiR2Files=file.path(Dir, FilePath)

names=c("4_Ago3", "1_Piwi4", "2_Piwi5", "3_Piwi6")

names(tapiR2Files)= names


for (i in 1:length(tapiR2Files)){
          x= read_tsv(tapiR2Files[i], col_names = TRUE) 
          y= log2(sum(sum(x$Count_IP)/ sum(x$Count_input)))
          assign(paste(names(tapiR2Files)[i], "tapiR2", sep="_"), y)
}

```



#### Plot enrichment of tapiR1/2

Enrichment of both tapiR1 and 2 over input in all four IPs

```{r enrichment, fig.width= 4}

enr= tibble(piRNA= rep(c("tapiR1", "tapiR2"), times=4),
            sample=rep(names, each=2),
            enrichment=c(`4_Ago3_tapiR1`, `4_Ago3_tapiR2`,
                         `1_Piwi4_tapiR1`, `1_Piwi4_tapiR2`,
                         `2_Piwi5_tapiR1`, `2_Piwi5_tapiR2`,
                         `3_Piwi6_tapiR1`, `3_Piwi6_tapiR2`))

ggplot(enr, aes(sample, enrichment, fill= piRNA, group=piRNA)) + 
      geom_bar(stat="identity", position = "dodge", color="black") +
      theme(axis.line = element_line(),
                panel.grid.major = element_blank(),
                panel.background = element_blank()) +
      scale_fill_manual(values=c( "#ABD9E9", "#4575B4")) +ylim(-2.5,5)


```


#### Piwi4 IP

Plot count of tapiR1 and 2, or other reads enriched in Piwi4 IP

```{r Piwi4, fig.width=3}

Dir  = "./IPseq/Raw"  #change to folder with data
FilePath = dir("./IPseq/Raw/", "RDVJ103.enriched")

IPFiles=file.path(Dir, FilePath)

Piw4IP= read_tsv(IPFiles, col_names = TRUE)


Piwi4IP  = Piw4IP %>% mutate(piRNA=ifelse(Chrom==3 & 
                                            (End==41157596 |
                                    				 End==41158652 |
                                    				 End==41158499 |
                                    				 End==41158348 |
                                    				 End==41158197 |
                                    				 End==41158047 |
                                    				 End==41157894 |
                                    				 End==41157744 |
                                    				 End==41157449 |
                                    				 End==41157301 |
                                    				 End==41157150 |
                                    				 End==41157002 |
                                    				 End==41156851 |
                                    				 End==41156703 |
                                    				 End==41156553 |
                                    				 End==41156405 |
                                    				 End==41156255 |
                                    				 End==41156105 |
                                    				 End==41155955 |
                                    				 End==41155805), "tapiR1", 
                                    ifelse(Chrom==3 & 
                                             (End==41158739 |
                                    				 End==41158593 |
                                    				 End==41158440 |
                                    				 End==41158289 |
                                    				 End==41158138 |
                                    				 End==41157988 |
                                    				 End==41157835 |
                                    				 End==41157685 |
                                    				 End==41157538 |
                                    				 End==41157390 |
                                    				 End==41157242 |
                                    				 End==41157091 |
                                    				 End==41156943 |
                                    				 End==41156792 |
                                    				 End==41156644 |
                                    				 End==41156494 |
                                    				 End==41156346 |
                                    				 End==41156196 |
                                    				 End==41156046 |
                                    				 End==41155896 |
                                    				 End==41155746), "tapiR2", "others"))) %>%
  
          group_by(piRNA) %>% 
          summarize(mean= mean(Corr_count)) %>% 
          mutate(mean= mean/sum(mean)) %>%
          add_column(IP= rep("Piwi4", 3)) %>% 
          mutate(piRNA= factor(piRNA, levels=c("tapiR1", "tapiR2", "others")))

ggplot(Piwi4IP, aes(IP, mean, fill=piRNA)) + 
          geom_bar(stat="identity", color="black") +
          theme(axis.line = element_line(),
                panel.grid.major = element_blank(),
                panel.background = element_blank()) +
          scale_fill_manual(values=c( "#ABD9E9", "#4575B4", "gray80"))
```
